---
title: "Analysis Code Documentation"
author: "Bak, Kwan-Young"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    theme: cosmo
    code_folding: show 
---

```{r setup, include=FALSE, eval=TRUE}
knitr::opts_chunk$set(eval = TRUE, echo = TRUE, warning = FALSE, cache = FALSE, cache.lazy = FALSE)
```

```bash
📁 FTCW_Risk_Perception/
├── Analysis Workflow.Rmd       # Main analysis script (reproduces all results)
├── Analysis-Workflow.html      # Rendered HTML of the main analysis
├── Variable Codebook.Rmd       # Variable mapping and data processing details
├── Variable-Codebook.html      # Rendered HTML of the variable codebook
│
├── 📁 data/
│   └── 23_08.xlsx              # Raw survey data (not publicly distributable)
│
├── 📁 figure/
│   ├── rel_imp.pdf             # ✓ Figure 2 (Manuscript)
│   ├── interaction_plot.pdf    # ✓ Figure 3 (Manuscript)
│   ├── missing_pattern.pdf     # ✓ Figure S1 (Appendix A)
│   ├── traceplot.pdf           # ✓ Figure S2 (Appendix A)
│   ├── modelplot_mice.pdf      # Internal diagnostic plot (not in manuscript)
│   └── mosaicplot.pdf          # ✓ Figure S3 (Appendix C)
│
└── 📁 latex_table/
    ├── table_1.txt             # ✓ Table 1 (Manuscript)
    ├── table_s2.txt            # ✓ Table S1 (Appendix A)
    ├── table_s3.txt            # ✓ Table S2 (Appendix B)
    ├── rp-mice.txt             # ✓ Table S3 (Appendix D)
    ├── rp-interaction.txt      # ✓ Table S4 (Appendix E)
    ├── rp-sensitivity-cog.txt  # ✓ Table S5 (Appendix F)
    └── rp-sensitivity-aff.txt  # ✓ Table S6 (Appendix F)
```

---


# Data preperation    

### Data Import 
```{r message=FALSE}
rm(list=ls())

library(readxl)
library(gridExtra)
library(ggplot2)
library(ggmosaic)
library(ggpubr)
library(tidyverse)
library(dplyr)
library(corrplot)
library(modelsummary)
library(ggeffects)
library(broom)
library(xtable)
library(pals)
library(naniar)
library(relaimpo)
library(vcd)
library(mice)
library(tidyr)
library(knitr)
library(kableExtra)

dat = read_xlsx("./data/23_08.xlsx")
dat0 = dat[,26:30]
dat1 = dat[,33:35]
dat2 = dat[,39]
dat3 = dat[,41:43]
dat = cbind(dat0, dat1, dat2, dat3)
colnames(dat)
```

## data refinement 
```{r}
dat = dat %>% rename(ara = ARA, age = AGE, sex = SEX, presid = BQ1,
                     aff = BQ5, cog = BQ6, exag = BQ7, ideo = XD4,
                     job = JOB, class = XD2, edu = XD3, wt = WT2)
colnames(dat)
```

```{r}
dim(dat)
size = nrow(dat)
dat %>% group_by(cog) %>% summarise(n = n(), prop = n() / size)
dat %>% group_by(aff) %>% summarise(n = n(), prop = n() / size)
dat %>% group_by(ara) %>% summarise(n = n(), prop = n() / size)
dat %>% group_by(age) %>% summarise(n = n(), prop = n() / size)
dat %>% group_by(sex) %>% summarise(n = n(), prop = n() / size)
dat %>% group_by(presid) %>% summarise(n = n(), prop = n() / size)
dat %>% group_by(exag) %>% summarise(n = n(), prop = n() / size)
dat %>% group_by(ideo) %>% summarise(n = n(), prop = n() / size)
dat %>% group_by(job) %>% summarise(n = n(), prop = n() / size)
dat %>% group_by(class) %>% summarise(n = n(), prop = n() / size)
dat %>% group_by(edu) %>% summarise(n = n(), prop = n() / size)
```


```{r}
# missing value handling 

dat$cog = replace(dat$cog, dat$cog==9999,NA)
dat$aff = replace(dat$aff, dat$aff==9999,NA)
dat$class = replace(dat$class, dat$class==9999,NA)
dat$edu = replace(dat$edu, dat$edu==9999,NA)

dat$presid = replace(dat$presid, dat$presid==9999,3) # 3 (neutral/unknown/refusal category)
dat$ideo = replace(dat$ideo, dat$ideo==9999,4) # 4 (unknown/refusal category)
dat$exag = replace(dat$exag, dat$exag==9999,3) # 3 (unknown/refusal category)


# scale reversals

## aff: Higher values = more worried
dat$aff = -(dat$aff - 5)
## cog: Higher values = higher perceived likelihood
dat$cog = -(dat$cog - 5)
## class: Higher values = higher economic status
dat$class = ifelse(dat$class %in% c(3, 4, 5), -(dat$class - 6), dat$class + 3)
```


```{r}
# Check the number of missing values in each column
colSums((is.na(dat)))

# Count rows with a missing value in either aff or cog
sum(is.na(dat$aff) | is.na(dat$cog))
summary(dat)

# missing data visualization 
vis_miss(dat)

data_na = dat[rowSums(is.na(dat)) == 0, ]
dim(data_na)
```

## Dataset Creation

```{r}
# data_na: Complete case analysis (n=917)
# Used for: Table 1, Figure 2, Figure 3, Table S3, Table S4
data_na = data_na %>% mutate(ara = as.factor(ara), age = as.factor(age), sex = as.factor(sex),
                       job = as.factor(job), ideo = as.factor(ideo), class = as.factor(class), 
                       edu = as.factor(edu), presid = as.factor(presid),exag = as.factor(exag))
dim(data_na)

# data: Full dataset with missing values (n=1,002)
# Used for: MICE imputation (Appendix A)
data = dat %>% mutate(ara = as.factor(ara), age = as.factor(age), sex = as.factor(sex),
                       job = as.factor(job), ideo = as.factor(ideo), class = as.factor(class), 
                       edu = as.factor(edu), presid = as.factor(presid),exag = as.factor(exag))
dim(data)
```

# Main Analysis

## Table S2 - Distributional Characteristics of the Data

```{r}
# ==============================================================================
# Table S2: Distributional Characteristics of the Data
# Role: Calculates frequency (N) and proportion (%) for all analytical variables
# Mapping: [Appendix B] Table S2
# Output: Saved as './latex table/table_s2.txt'
# ==============================================================================

dim(data_na)
size = nrow(data_na)
data_na %>% group_by(cog) %>% summarise(n = n(), prop = n() / size)
data_na %>% group_by(aff) %>% summarise(n = n(), prop = n() / size)
data_na %>% group_by(ara) %>% summarise(n = n(), prop = n() / size)
data_na %>% group_by(age) %>% summarise(n = n(), prop = n() / size)
data_na %>% group_by(sex) %>% summarise(n = n(), prop = n() / size)
data_na %>% group_by(presid) %>% summarise(n = n(), prop = n() / size)
data_na %>% group_by(exag) %>% summarise(n = n(), prop = n() / size)
data_na %>% group_by(ideo) %>% summarise(n = n(), prop = n() / size)
data_na %>% group_by(job) %>% summarise(n = n(), prop = n() / size)
data_na %>% group_by(class) %>% summarise(n = n(), prop = n() / size)
data_na %>% group_by(edu) %>% summarise(n = n(), prop = n() / size)

get_summary_df = function(data, var_name, label) {
  data %>%
    group_by(!!sym(var_name)) %>%
    summarise(N = n(), Prop = n() / nrow(data)) %>%
    mutate(Variable = label) %>%
    mutate(Category = as.character(!!sym(var_name))) %>% 
    dplyr::select(Variable, Category, N, Prop)
}

table_s2_data = bind_rows(
  get_summary_df(data_na, "cog", "Cognitive risk perception"),
  get_summary_df(data_na, "aff", "Affective risk perception"),
  get_summary_df(data_na, "ara", "Residential area"),
  get_summary_df(data_na, "sex", "Sex"),
  get_summary_df(data_na, "age", "Age"),
  get_summary_df(data_na, "job", "Occupation"),
  get_summary_df(data_na, "class", "Economic status"),
  get_summary_df(data_na, "edu", "Educational attainment"),
  get_summary_df(data_na, "ideo", "Political ideologies"),
  get_summary_df(data_na, "presid", "Government trust"),
  get_summary_df(data_na, "exag", "Information trust")
)

sink(file = "./latex table/table_s2.txt")

print(xtable(table_s2_data, 
             digits = c(0, 0, 0, 0, 3), 
             caption = "Distributional characteristics of the data",
             label = "tab:table_s2"),
      include.rownames = FALSE,
      hline.after = c(-1, 0, nrow(table_s2_data)),
      comment = FALSE)

sink(file = NULL)
```

## Table 1 - Regression analysis of cognitive and affective RP

```{r}
# ==============================================================================
# Table 1: Regression analysis of cognitive and affective RP
# Role: Coefficient estimates from the regression analysis of cognitive and affective RP
# Mapping: [Manuscript] Table 1
# Output: Saved as './latex table/table_1.txt'
# ==============================================================================

fit_cog_na = lm(cog ~ ara + age + sex + presid + exag + ideo + job + class + edu, 
                data = data_na, weights = data_na$wt)
fit_aff_na = lm(aff ~ ara + age + sex + presid + exag + ideo + job + class + edu, 
                      data = data_na, weights = data_na$wt)
summary(fit_cog_na)
summary(fit_aff_na)

sink(file = "./latex table/table_1.txt")
models_main = list("Cognitive RP" = fit_cog_na, 
                   "Affective RP" = fit_aff_na)

modelsummary(models_main,
             fmt = 2,
             stars = TRUE,
             statistic = NULL,
             estimate = "{estimate}{stars} [{conf.low}, {conf.high}]",
             coef_omit = "Intercept",
             gof_omit = 'Num.Obs.|DF|Deviance|F|Log.Lik.|RMSE|AIC|BIC',
             title = 'Coefficient estimates for main regression analysis (Table 1).',
             output = "latex",
             note = list("+ p < 0.1, * p < 0.05, ** p < 0.01, *** p < 0.001"))
sink(file = NULL)
```

## Figure 2 - Relative Importance

```{r}
# ==============================================================================
# Figure 2: Relative Importance 
# Role: Quantifies the contribution of each predictor to the model
# Mapping: [Manuscript] Figure 2
# Output: Saved as './figure/rel_imp.pdf'
# ==============================================================================

pdf("./figure/rel_imp.pdf", width = 12, height = 6)

target_order = c("age", "economic status", "educational attainment", 
                 "occupation", "political ideologies", "residential area", 
                 "sex", "trust in government", "trust in information")

## Cognitive RP
cog_vi = calc.relimp(fit_cog_na, type = "lmg", no.CI = TRUE)

cog_vi_lmg = cog_vi$lmg
cog_vi_lmg = tibble(var = names(cog_vi_lmg), imp = cog_vi_lmg)

cog_vi_lmg = cog_vi_lmg %>% 
   mutate(var = case_when(
      var == "ara" ~ "residential area", 
      var == "age" ~ "age",
      var == "sex" ~ "sex",
      var == "job" ~ "occupation",
      var == "class" ~ "economic status",
      var == "edu" ~ "educational attainment",
      var == "presid" ~ "trust in government",
      var == "exag" ~ "trust in information",
      var == "ideo" ~ "political ideologies"
   )) %>%
   mutate(var = factor(var, levels = rev(target_order)))

r1 = ggplot(cog_vi_lmg, aes(x = imp, y = var)) + 
   geom_segment(aes(xend = 0, yend = var), col = "blue", linewidth = 1) + 
   geom_point(col = "blue", size = 3) +
   xlim(c(0, 0.3)) + 
   xlab("") + 
   ylab("") + 
   theme_bw(base_size = 15) + 
   ggtitle("Cognitive RP") +
   theme(axis.text.y = element_text(vjust = 0.5, size = 13))

## Affective RP
aff_vi = calc.relimp(fit_aff_na, type = "lmg", no.CI = TRUE)

aff_vi_lmg = aff_vi$lmg 
aff_vi_lmg = tibble(var = names(aff_vi_lmg), imp = aff_vi_lmg)

aff_vi_lmg = aff_vi_lmg %>% 
   mutate(var = case_when(
      var == "ara" ~ "residential area", 
      var == "age" ~ "age",
      var == "sex" ~ "sex",
      var == "job" ~ "occupation",
      var == "class" ~ "economic status",
      var == "edu" ~ "educational attainment",
      var == "presid" ~ "trust in government",
      var == "exag" ~ "trust in information",
      var == "ideo" ~ "political ideologies"
   )) %>%
   mutate(var = factor(var, levels = rev(target_order)))

r2 = ggplot(aff_vi_lmg, aes(x = imp, y = var)) + 
   geom_segment(aes(xend = 0, yend = var), col = "blue", linewidth = 1) + 
   geom_point(col = "blue", size = 3) +
   xlim(c(0, 0.3)) +
   xlab("") + 
   ylab("") +
   theme_bw(base_size = 15) + 
   ggtitle("Affective RP") +
   theme(axis.text.y = element_text(vjust = 0.5, size = 13))

grid.arrange(r1, r2, ncol = 2)
dev.off()
```


## Figure 3 - Interaction Effects

```{r message=FALSE}
# ==============================================================================
# Figure 3: Interaction Effects
# Role: Visualizes the interactive association between Government Trust (GT) 
#       and Information Trust (IT) on risk perceptions
# Mapping: [Manuscript] Figure 3
# Output: Saved as './figure/interaction_plot.pdf'
# ==============================================================================

# Fit regression models including the interaction term (presid * exag)
# Interaction terms test if the effect of GT varies depending on the level of IT

fit_cog_int = lm(cog ~ ara + age + sex + presid + exag + ideo + job + class + edu + presid*exag, data = data_na, weights = wt)
fit_aff_int = lm(aff ~ ara + age + sex + presid + exag + ideo + job + class + edu + presid*exag, data = data_na, weights = wt)

summary(fit_cog_int)
summary(fit_aff_int)


## Visualization 

barplot_df = data_na %>% mutate(cog = as.numeric(cog), aff = as.numeric(aff)) %>% group_by(presid, exag) %>% summarise(cog = mean(cog), aff = mean(aff))

theme_set(theme_bw())

pdf("./figure/interaction_plot.pdf", width = 27, height = 15)

# Create data frame with all 9 combinations (3 GT levels × 3 IT levels)
presid_data1 = data.frame(
  presid = factor(rep(1:3, each = 3)),
  exag = factor(rep(1:3, 3)),
  estimate = c(
    0, 
    coef(fit_cog_int)["exag2"],
    coef(fit_cog_int)["exag3"],
    coef(fit_cog_int)["presid2"],
    coef(fit_cog_int)["presid2"] + coef(fit_cog_int)["exag2"] + coef(fit_cog_int)["presid2:exag2"],
    coef(fit_cog_int)["presid2"] + coef(fit_cog_int)["exag3"] + coef(fit_cog_int)["presid2:exag3"],
    coef(fit_cog_int)["presid3"],
    coef(fit_cog_int)["presid3"] + coef(fit_cog_int)["exag2"] + coef(fit_cog_int)["presid3:exag2"],
    coef(fit_cog_int)["presid3"] + coef(fit_cog_int)["exag3"] + coef(fit_cog_int)["presid3:exag3"]
  )
)

plot1 = ggplot(presid_data1, aes(x = presid, y = estimate, color = exag, group = exag)) +
  geom_line(size = 1.5) +  
  geom_point() +
  labs(x = "Trust in government",
       y = "Estimated Effect for Cognitive RP",
       color = "") +
  scale_x_discrete(labels = c("well done", "poorly done", "neutral/unknown/refusal")) +
  scale_color_manual(values=c('#8B0000', '#00008B', '#006400'),
                    labels = c("exaggerated", "not exaggerated", "unknown/refusal")) +
  theme(axis.title.x = element_text(size = 40, margin = margin(t = 20, b = 10)),
          axis.title.y = element_text(size = 35, margin = margin(l = 10, r = 15)),
          axis.text.x = element_text(size = 32),
          axis.text.y =element_text(size = 25),
          axis.ticks.y=element_blank(),
          legend.text = element_text(size = 32),
          panel.border = element_rect(color = "black", fill = NA, size = 0.5)) +
  guides(color = guide_legend(override.aes = list(size = 7))) +
  ylim(0,2)


presid_data2 = data.frame(
  presid = factor(rep(1:3, each = 3)),
  exag = factor(rep(1:3, 3)),
  estimate = c(
    0, 
    coef(fit_aff_int)["exag2"],
    coef(fit_aff_int)["exag3"],
    coef(fit_aff_int)["presid2"],
    coef(fit_aff_int)["presid2"] + coef(fit_aff_int)["exag2"] + coef(fit_aff_int)["presid2:exag2"],
    coef(fit_aff_int)["presid2"] + coef(fit_aff_int)["exag3"] + coef(fit_aff_int)["presid2:exag3"],
    coef(fit_aff_int)["presid3"],
    coef(fit_aff_int)["presid3"] + coef(fit_aff_int)["exag2"] + coef(fit_aff_int)["presid3:exag2"],
    coef(fit_aff_int)["presid3"] + coef(fit_aff_int)["exag3"] + coef(fit_aff_int)["presid3:exag3"]
  )
)

plot2 = ggplot(presid_data2, aes(x = presid, y = estimate, color = exag, group = exag)) +
  geom_line(size = 1.5) +
  geom_point() +
  labs(x = "Trust in government",
       y = "Estimated Effect for Affective RP",
       color = "") +
  scale_x_discrete(labels = c("well done", "poorly done", "neutral/unknown/refusal")) +
  scale_color_manual(values=c('#8B0000', '#00008B', '#006400'),
                    labels = c("exaggerated", "not exaggerated", "unknown/refusal")) +
  theme(axis.title.x = element_text(size = 40, margin = margin(t = 20, b = 10)),
          axis.title.y = element_text(size = 35, margin = margin(l = 10, r = 15)),
          axis.text.x = element_text(size = 32),
          axis.text.y =element_text(size = 25),
          axis.ticks.y=element_blank(),
          legend.text = element_text(size = 32),
          panel.border = element_rect(color = "black", fill = NA, size = 0.5))+
  guides(color = guide_legend(override.aes = list(size = 7))) +
  ylim(0, 2) 

ggarrange(plot1, plot2, ncol=2, common.legend = TRUE, legend="top")
dev.off()
```



# Multiple Imputation Analysis

## Appendix A - Figures S1

```{r}
# ==============================================================================
# Appendix A Figure S1: Missing Data Pattern 
# Role: Visualizes the structure and frequency of missing values in the dataset
# Mapping: [Appendix A] Figures S1
# Output: Saved as './figure/missing_pattern.pdf'
# ==============================================================================

# Define the matrix for manual missing pattern visualization
missing_mat = matrix(0, nrow = 12, ncol = 11)
missing_mat[2, 11] = missing_mat[3, 10] = missing_mat[4, 10:11] = missing_mat[5, 9] =
  missing_mat[6, c(9,11)] = missing_mat[7, 9:10] = missing_mat[8, 9:11] =
  missing_mat[9, 8] = missing_mat[10, c(8, 11)] = missing_mat[11, c(8,10,11)] =
  missing_mat[12, 8:9] = 1

missing_mat = t(missing_mat)

pdf("./figure/missing_pattern.pdf", width = 8, height = 6)

ggplot(reshape2::melt(missing_mat)) +
  geom_tile(aes(x = Var2, y = Var1, fill = value), color = "white") + 
  scale_fill_gradient(low = "lightgray", high = "navy") +
  theme_void() + theme(legend.position = "none") +
  annotate("text", x = 0, y = 1:11, label = c("residential area", "age", "sex", "trust in government", "trust in information", "political ideologies",  "occupation", "educational attainment", "economic status", "affective RP", "cognitive RP"), hjust = 1, vjust = 0.5) +
  annotate("text", x = 1:12, y = 12, label = c("917", "47", "7", "6", "9", "1", "1", "4", "5", "2", "1", "2"), hjust = 0.5, vjust = 0.5) + 
  annotate("text", x = 1:12, y = 0, label = c("0", "1", "1", "2", "1", "2", "2", "3", "1", "2", "3", "2"), hjust = 0.5, vjust = 0.5) +
  annotate("text", x = 13, y = 1:12, label = c("0", "0", "0", "0", "0", "0", "0", "10", "17", "19", "61", "107"), hjust = 0.5, vjust = 0.5) +
  xlim(c(-3, 13))

dev.off()
```

## Appendix A - Figures S2

```{r}
# ==============================================================================
# Appendix A Figure S2: Trace plots for the multiple imputation model
# Role: Performs Multivariate Imputation by Chained Equations (MICE) and 
#       generates trace plots to ensure algorithm convergence.
# Mapping: [Appendix A] Figures S2
# Output: Saved as './figure/traceplot.pdf'
# ==============================================================================

# Execute MICE algorithm: m=10 datasets, 10 iterations
imp_data = mice(data = data, m = 10, maxit = 10, seed = 185, print = FALSE)

# Diagnostics: Check convergence via trace plots (mean and sd of imputed values)
get_trace_df = function(imp_obj) 
{
  # mean
  mean_dat = as.data.frame.table(imp_obj$chainMean)
  colnames(mean_dat) = c("variable", "iteration", "chain", "value")
  mean_dat$measure = "mean"
  
  # sd
  sd_dat = as.data.frame.table(sqrt(imp_obj$chainVar))
  colnames(sd_dat) = c("variable", "iteration", "chain", "value")
  sd_dat$measure = "sd"
  
  bind_rows(mean_dat, sd_dat)
}

trace_data = get_trace_df(imp_data) 

# Select key variables for Figure S2 visualization
plot_data = trace_data %>%
  filter(variable %in% c("aff", "cog", "class", "edu")) %>%
  mutate(
    variable = recode(variable, "aff" = "Affective RP", "cog" = "Cognitive RP", "class" = "economic status", "edu" = "educational attainment"),
    iteration = as.numeric(iteration) 
  )

# Plotting trace plots
ggplot(plot_data, aes(x = iteration, y = value, color = chain, group = chain)) +
  geom_line(alpha = 0.8) + 
  facet_grid(variable ~ measure, scales = "free") + 
  theme_bw() + labs(x = "Iteration", y = NULL) +
  theme(legend.position = "none", strip.text = element_text(face = "bold", size = 11), panel.grid = element_blank())

ggsave("./figure/traceplot.pdf", width = 6, height = 8)
```


## Table S1 - multiple imputation regression model fitting

```{r}
# ==============================================================================
# Appendix A Table S1: Multiple Imputation Regression 
# Role: Fits regression models to each of the 10 imputed datasets and pools 
#       the results to obtain robust estimates, accounting for missing data
# Mapping: [Appendix A] Table S1
# Output: Saved as './latex table/rp-mice.txt'
# ==============================================================================

# Fit linear models to the imputed data and pool the results
# Cognitive (CRP)
fit_cog_mice = with(imp_data, lm(cog ~ ara + age + sex + presid + exag +
                                 ideo + job + class + edu, weights = wt))
fit_cog = pool(fit_cog_mice)
summary(fit_cog)
pool.r.squared(fit_cog)


# Affective RP
fit_aff_mice = with(imp_data, lm(aff ~ ara + age + sex + presid + exag +
                                 ideo + job + class + edu, weights = wt))
fit_aff = pool(fit_aff_mice)
summary(fit_aff)
pool.r.squared(fit_aff)


sink(file = "./latex table/rp-mice.txt")
models = list("Cognitive RP" = fit_cog, 
              "Affective RP" = fit_aff)
modelsummary(models,
             fmt = 2,
             stars = TRUE,
             statistic = NULL,
             estimate = c("{estimate}{stars} [{conf.low}, {conf.high}]"),
             #estimate = c("{estimate}{stars} ({p.value})"),
             coef_omit = "Intercept",
             gof_omit = 'Num.Obs.|DF|Deviance|F|Log.Lik.|RMSE|AIC|BIC',
             title = 'Coefficients estimates (with confidence intervals in parantheses) of multiple imputation regression analysis for cognitive and affective risk perception.',
             output = "latex",
             note = list("+ p $<$ 0.1, * p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001"))
sink(file = NULL)


# Visualize pooled coefficient estimates (Model Plot)

pdf("./figure/modelplot_mice.pdf", width = 12, height = 6)
  
p1 = modelplot(fit_cog, conf_level = .95, coef_omit = "Intercept") +
   aes(color = ifelse(p.value < 0.05, "Significant", "Not significant")) +
   scale_color_manual(values = c("gray", "blue")) +
   geom_vline(xintercept = 0, color = 'orange') +
   guides(color=guide_legend(title="Significance")) +
   theme(legend.position = "none") +
   xlim(c(-1, 1.2)) +
   ggtitle("Cognitive RP")

p2 = modelplot(fit_aff, conf_level = .95, coef_omit = "Intercept") +
   aes(color = ifelse(p.value < 0.05, "Significant", "Not significant")) +
   scale_color_manual(values = c("gray", "blue")) +
   geom_vline(xintercept = 0, color = 'orange') +
   guides(color=guide_legend(title="Significance")) +
   theme(legend.position = "none") +
   xlim(c(-1, 1.2)) +
   ggtitle("Affective RP")

grid.arrange(p1, p2, ncol = 2)
dev.off()
```


```{r message=FALSE}
# ------------------------------------------------------------------------------
# Pooled Correlation Analysis 
# Role: Calculates the pooled Pearson and Spearman correlations between CRP and ARP 
#       across all imputed datasets to validate the relationship between the two DVs.
# Output: Correlation coefficients displayed in the R Console
# ------------------------------------------------------------------------------

library(psych)
library(mitools)
library(miceadds)

miceadds::micombine.cor(mi.res = imp_data, variables = c("cog", "aff"), method = "pearson")
miceadds::micombine.cor(mi.res = imp_data, variables = c("cog", "aff"), method = "spearman")
```


## Figure S3 - mosaic plot 

```{r}
# ==============================================================================
# Figure S3: Mosaic Plot of Trust Associations
# Role: Visualizes the conditional distribution and associational relationship between GT and IT
# Mapping: [Appendix C] Figure S3
# Output: Saved as './figure/mosaicplot.pdf'.
# ==============================================================================

data_complete = data_na %>% mutate(cog = factor(cog), aff = factor(aff))
data_complete$presid = factor(data_complete$presid, levels = c(1, 2, 3),
                          labels = c("well done", "poorly done", "neutral/unknown/refusal"))

theme_set(theme_bw())

pdf("./figure/mosaicplot.pdf", width = 12, height = 8)

ggplot(data = data_complete) + 
    geom_mosaic(aes(x = product(exag, presid), fill = exag)) + 
    theme_minimal() +
    scale_x_productlist(name = "Trust in government") + 
    scale_y_productlist(name = "Trust in information") + 
    labs(fill = "exag") +
    theme(axis.title.x = element_text(size = 25, margin = margin(t = 20, b = 10)),
          axis.title.y = element_text(size = 25, margin = margin(l = 10, r = 15)),
          axis.text.x = element_text(size = 20),
          axis.text.y = element_blank(),
          axis.ticks.y=element_blank(),
          legend.text = element_text(size = 17),
          panel.border = element_rect(color = "black", fill = NA, size = 0.5)) +
    scale_fill_manual(' ', values=c('#8B0000', '#00008B', '#006400'),
                      labels = c("exaggerated", "not exaggerated", "unknown/refusal")) 

dev.off()
```


## Table S3: Association between government and information trust

```{r}
# ==============================================================================
# Table S3: Association between Government and Information Trust
# Role: Creates a cross-tabulation table showing the frequency and row-wise 
#       percentage to analyze the relationship between GT and IT
# Mapping: [Appendix D] Table S3
# Output: Saved as './latex table/table_s3.txt'
# ==============================================================================

# Generate the contingency table with frequency and percentage
table_s3 = data_na %>%
  mutate(
    presid = factor(presid, levels = c(1, 2, 3), 
                    labels = c("Well done", "Poorly done", "Neutral/unknown/refusal")),
    exag = factor(exag, levels = c(1, 2, 3), 
                  labels = c("exaggerated", "not exaggerated", "unknown/refusal"))
  ) %>%
  count(presid, exag) %>%
  group_by(presid) %>%
  mutate(
    pct = n / sum(n) * 100,
    cell = sprintf("%d (%.1f%%)", n, pct) 
  ) %>%
  dplyr::select(presid, exag, cell) %>% 
  pivot_wider(names_from = exag, values_from = cell)

# Add Row Totals
totals = data_na %>%
  mutate(presid = factor(presid, levels = c(1, 2, 3), 
                         labels = c("Well done", "Poorly done", "Neutral/unknown/refusal"))) %>%
  count(presid) %>%
  rename(Total = n)

table_s3 = table_s3 %>% left_join(totals, by = "presid")

sink(file = "./latex table/table_s3.txt")

print(xtable(table_s3, 
             caption = "Association between government and information trust",
             label = "tab:table_s3"),
      include.rownames = FALSE,
      hline.after = c(-1, 0, nrow(table_s3)),
      comment = FALSE)

sink(file = NULL)

print(table_s3)
```

## Table S4: Regression models including the interaction

```{r}
# ==============================================================================
# Table S4: Regression Models Including the Interaction
# Role: Summarizes the full regression results for models containing the interaction term between GT and IT
# Mapping:  [Appendix E] Table S4
# Output: Saved as './latex table/rp-interaction.txt'
# ==============================================================================

models_int = list("Cognitive RP" = fit_cog_int, 
                  "Affective RP" = fit_aff_int)

sink(file = "./latex table/rp-interaction.txt")
modelsummary(models_int,
             fmt = 2,
             stars = TRUE,
             statistic = NULL,
             estimate = c("{estimate}{stars} [{conf.low}, {conf.high}]"),
             coef_omit = "Intercept",
             gof_omit = 'Num.Obs.|DF|Deviance|F|Log.Lik.|RMSE|AIC|BIC',
             title = 'Coefficient estimates (with confidence intervals in parentheses) of regression analysis for cognitive and affective risk perception including the interaction between government and information trust.',
             output = "latex",
             note = list("+ p < 0.1, * p < 0.05, ** p < 0.01, *** p < 0.001"))
sink(file = NULL)
```

## Table S5 and Table S6: Sensitivity analysis with respect to information trust (IT)
```{r}
# ==============================================================================
# Table S5: Sensitivity analyses for cognitive risk perception across alternative model specifications
# Table S6: Sensitivity analyses for affective risk perception across alternative model specifications
# Role: Sensitivity analyses assessing the robustness of the results to the inclusion of information trust (IT), which may conceptually overlap with risk perception. 
# Mapping:  [Appendix F] Table S5 and Table S6
# Output: Saved as './latex table/rp-sensitivity-cog.txt' and './latex table/rp-sensitivity-aff.txt'
# ==============================================================================

fit_cog_full = lm(
  cog ~ ara + age + sex + presid + exag + ideo + job + class + edu + presid*exag,
  data = data_na,
  weights = wt
)

fit_cog_main = lm(
  cog ~ ara + age + sex + presid + exag + ideo + job + class + edu,
  data = data_na,
  weights = wt
)

fit_cog_noIT = lm(
  cog ~ ara + age + sex + presid + ideo + job + class + edu,
  data = data_na,
  weights = wt
)

fit_aff_full = lm(
  aff ~ ara + age + sex + presid + exag + ideo + job + class + edu + presid*exag,
  data = data_na,
  weights = wt
)

fit_aff_main = lm(
  aff ~ ara + age + sex + presid + exag + ideo + job + class + edu,
  data = data_na,
  weights = wt
)

fit_aff_noIT = lm(
  aff ~ ara + age + sex + presid + ideo + job + class + edu,
  data = data_na,
  weights = wt
)

models_cog = list(
  "Full" = fit_cog_full,
  "No interaction" = fit_cog_main,
  "No IT" = fit_cog_noIT
)

sink(file = "./latex table/rp-sensitivity-cog.txt")

modelsummary(
  models_cog,
  fmt = 2,
  stars = TRUE,
  statistic = NULL,
  estimate = "{estimate}{stars} [{conf.low}, {conf.high}]",
  coef_omit = "Intercept",
  gof_omit = "Num.Obs.|DF|Deviance|F|Log.Lik.|RMSE|AIC|BIC",
  title = "Cognitive risk perception: sensitivity analysis across alternative model specifications.",
  output = "latex",
  notes = list("+ p < 0.1, * p < 0.05, ** p < 0.01, *** p < 0.001")
)

sink(file = NULL)


models_aff = list(
  "Full" = fit_aff_full,
  "No interaction" = fit_aff_main,
  "No IT" = fit_aff_noIT
)

sink(file = "./latex table/rp-sensitivity-aff.txt")

modelsummary(
  models_aff,
  fmt = 2,
  stars = TRUE,
  statistic = NULL,
  estimate = "{estimate}{stars} [{conf.low}, {conf.high}]",
  coef_omit = "Intercept",
  gof_omit = "Num.Obs.|DF|Deviance|F|Log.Lik.|RMSE|AIC|BIC",
  title = "Affective risk perception: sensitivity analysis across alternative model specifications.",
  output = "latex",
  notes = list("+ p < 0.1, * p < 0.05, ** p < 0.01, *** p < 0.001")
)

sink(file = NULL)
```