---
title: "Variable Codebook"
author: "Bak, Kwan-Young"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    theme: cosmo
    code_folding: hide
  pdf_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(knitr)
library(kableExtra)
```

# Overview

This document provides a comprehensive mapping between variable names used in the manuscript and those used in the R analysis code for the study: **"Role of government and information trust in public perception of environmental risk: a case study of treated contaminated water discharge in Fukushima"**.

---

# Main Variable Mapping

```{r main_mapping}
variable_mapping = tibble(
  `Manuscript Variable` = c(
    "Cognitive risk perception (CRP)",
    "Affective risk perception (ARP)",
    "Government trust (GT)",
    "Information trust (IT)",
    "Residential area",
    "Sex",
    "Age",
    "Occupation",
    "Economic status",
    "Educational attainment",
    "Political ideologies",
    "Weight"
  ),
  
  `Code Variable` = c(
    "cog", "aff", "presid", "exag", "ara", "sex", 
    "age", "job", "class", "edu", "ideo", "wt"
  ),
  
  `Survey Code` = c(
    "BQ6", "BQ5", "BQ1", "BQ7", "ARA", "SEX", 
    "AGE", "JOB", "XD2", "XD3", "XD4", "WT2"
  )
)

kable(variable_mapping, 
      caption = "Primary Variable Mapping",
      booktabs = TRUE) %>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>%
  column_spec(1, bold = TRUE, width = "8cm") %>%
  column_spec(2, monospace = TRUE, color = "darkblue", width = "3cm") %>%
  column_spec(3, monospace = TRUE, color = "darkgreen", width = "3cm")
```

---

# Data Transformations

## Missing Value Handling

```{r missing_handling}
missing_handling = tibble(
  Variable = c("cog", "aff", "class", "edu", "presid", "ideo", "exag"),
  `Original Missing Code` = c("9999", "9999", "9999", "9999", "9999", "9999", "9999"),
  `Transformation` = c("NA", "NA", "NA", "NA", "3", "4", "3"),
  Rationale = c(
    "Missing response - excluded from analysis",
    "Missing response - excluded from analysis",
    "Missing response - excluded from analysis",
    "Missing response - excluded from analysis",
    "Neutral/unknown category created",
    "Unknown/refusal category created",
    "Unknown/refusal category created"
  )
)

kable(missing_handling, 
      caption = "Missing Value Handling Strategy") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

## Scale Reversals

```{r reversals}
reversal_info = tibble(
  Variable = c("cog", "aff"),
  `Original Scale` = c("1=very likely, 4=not at all likely",
                       "1=very worried, 4=not worried at all"),
  `Transformation` = c("-(cog - 5)", "-(aff - 5)"),
  `New Scale` = c("1=not at all likely, 4=very likely",
                  "1=not worried at all, 4=very worried"),
  Reason = c("Align with intuitive interpretation (higher = higher risk)",
             "Align with intuitive interpretation (higher = more worried)")
)

kable(reversal_info, 
      caption = "Scale Reversal Transformations") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

## Economic Status Recoding

```{r class_recode}
cat("Original coding scheme (XD2):")
cat("\n1 = Upper")
cat("\n2 = Upper middle")
cat("\n3 = Middle")
cat("\n4 = Lower middle")
cat("\n5 = Lower")
cat("\n\nTransformation in R:")
cat("\nclass = ifelse(class %in% c(3, 4, 5), -(class - 6), class + 3)")
cat("\n\nFinal coding:")
cat("\n1 = Lower")
cat("\n2 = Lower middle")
cat("\n3 = Middle")
cat("\n4 = Upper/Upper middle")
```

---

# Category Labels

## Residential Area (ara)

```{r ara_labels}
ara_df = tibble(
  Code = 1:8,
  Label = c("Seoul", "Incheon/Gyeonggi", "Gangwon", 
            "Daejeon/Sejong/Chungcheong", "Gwangju/Jeolla", 
            "Daegu/Gyeongbuk", "Busan/Ulsan/Gyeongnam", "Jeju")
)
kable(ara_df) %>% kable_styling(bootstrap_options = c("striped", "hover"))
```

## Age Groups (age)

```{r age_labels}
age_df = tibble(
  Code = 1:6,
  `Age Range` = c("18-29", "30-39", "40-49", "50-59", "60-69", "70+")
)
kable(age_df) %>% kable_styling(bootstrap_options = c("striped", "hover"))
```

## Occupation (job)

```{r job_labels}
job_df = tibble(
  Code = 1:7,
  Category = c("Agriculture/fishery/forestry", "Self-employed", 
               "Skilled labor/service", "Office/administration", 
               "Homemaker", "Student", "Unemployed/other")
)
kable(job_df) %>% kable_styling(bootstrap_options = c("striped", "hover"))
```

## Government Trust (presid)

```{r presid_labels}
presid_df = tibble(
  Code = 1:3,
  Category = c("Well done", "Poorly done", "Neutral/unknown/refusal"),
  `Baseline in Models` = c("Yes (reference)", "No", "No")
)
kable(presid_df) %>% kable_styling(bootstrap_options = c("striped", "hover"))
```

## Information Trust (exag)

```{r exag_labels}
exag_df = tibble(
  Code = 1:3,
  Category = c("Exaggerated", "Not exaggerated", "Unknown/refusal"),
  `Baseline in Models` = c("Yes (reference)", "No", "No")
)
kable(exag_df) %>% kable_styling(bootstrap_options = c("striped", "hover"))
```

---

# Sample Sizes

```{r sample_info}
sample_info = tibble(
  Stage = c("Original survey", "Risk perception responses", 
            "Complete case (main analysis)", "MICE imputation"),
  N = c(1002, 933, 917, "10 × 1002"),
  Description = c("Total participants", 
                  "Participants who answered risk perception questions",
                  "Listwise deletion of missing values",
                  "Multiple imputation datasets")
)

kable(sample_info, 
      caption = "Sample Size by Analysis Stage") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```
